---
title: "Embedding regression"
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages 

```{r}

# Import pkgs
pacman::p_load(
  tidyverse,
  lubridate, 
  purrr,
  furrr,
  tm,
  quanteda, 
  here,
  tidytext, # text analysis 
  textclean,
  textstem, 
  ggthemes,
  text2vec, # word embedding 
  widyr,
  patchwork, # arranging ggplots
  glue,
  # deep learning 
  text2vec,
  # network graph
  igraph,
  ggraph,
  # structural breakpoint
  strucchange,
  pbapply,
  kableExtra
)

devtools::install_github("prodriguezsosa/conText")

library(conText)

theme_set(theme_clean())

source(here("functions", "embedding.r"))
```


## Load data 

```{r}
df <- read.csv(here("processed_data/cleaned_text.csv")) 

df <- df %>%
  mutate(group = if_else(str_detect(source, "Arab"), "Arab", "Indian"))

df <- df %>%
  select(c("text","source","date", "group"))

filipino <- read.csv(here("processed_data", "filipino.csv")) %>%
  select(c("text","source","date")) %>%
  mutate(group = "Filipino")

aapi <- read.csv(here("processed_data", "aapi.csv")) %>%
  select(c("text","source","date")) %>%
  mutate(group = "AAPI")

aapi$date <- dmy(aapi$date)
filipino$date <- dmy(filipino$date)

df$date <- as.Date(df$date)
```

```{r}
corpus <- bind_rows(df, filipino, aapi)

unique(corpus$group)
```

```{r}
# Create dummy variables 
corpus$intervention <- if_else(corpus$date >= as.Date("2001-09-11"), 1, 0)

write.csv(corpus, here("processed_data", "corpus.csv"))
```

## Preproceessing text 

```{r}
corpus$clean_text <- clean_text(corpus$text)

corpus <- corpus %>% 
  filter(!str_detect(clean_text, "film|cartoon|festival|music|dance"))

corpus_copy <- corpus
```

# Arab + Indian  

## Subsetted data 

```{r}
corpus <- corpus_copy %>%
  filter(group %in% c("Arab", "Indian")) %>%
  mutate(group = if_else(str_detect(group, "Arab"), 1, 0))
```

## Local embedding and matrix 

```{r}
set.seed(20201008L)
local_glove <- df2vec(corpus)
local_transform <- df2ltm(corpus, local_glove)

save(local_glove, local_transform, 
     file = here("processed_data/context_bg_ai.Rdata"))
```

## ALC embedding approach 


```{r}
mod1 <- conText(formula = terror ~ intervention + group, 
          data = corpus, 
          text_var = 'clean_text', 
          pre_trained = local_glove,
          transform = TRUE, 
          transform_matrix = local_transform, 
          bootstrap = TRUE, 
          num_bootstraps = 20, 
          stratify_by = c('intervention', 'group'),
          permute = TRUE, 
          num_permutations = 200, 
          window = 6, 
          valuetype = 'fixed', 
          case_insensitive = TRUE, 
          hard_cut = FALSE,
          verbose = FALSE)

plot_tibble1 <- mod1$normed_betas %>% 
  mutate(Coefficient = c("9/11 attacks", "Arab American")) %>% 
  mutate(Coefficient = factor(Coefficient, levels = Coefficient))

kable(plot_tibble1)
```
Coefficient	Normed_Estimate	Std.Error	Empirical_Pvalue
9/11 attacks	0.1232869	0.0013949	0
Arab American	0.2121369	0.0016851	0

```{r}
reg_plot1 <- plot_tibble1 %>%
  ggplot(aes(x = Coefficient, y = Normed_Estimate)) + 
  geom_bar(position = position_dodge(), 
    stat = "identity", width = 0.5) + 
  geom_errorbar(aes(ymin = Normed_Estimate - 
    1.96 * Std.Error, ymax = Normed_Estimate + 1.96 * Std.Error), size = 0.75, width = 0.15, 
    position = position_dodge(0.9)) + 
  ylab("Norm of beta hats") + 
  theme(axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 1),
          axis.text.y = element_text(size = 10)) +
  labs(
    title = "Arab and Indian Amerian newspaper comparison",
    subtitle = "Keyword: Terror")

reg_plot1

ggsave(here("output", "embedreg_ai.png"))
```

## Nearest neighbors 

```{r}
set.seed(20201008L)
arab_post_bt <- get_bt_terms(1, 1, "terror", 200, "Arab Americans", "Indian Americans")
indian_post_bt <- get_bt_terms(1, 0, "terror", 200, "Arab Americans", "Indian Americans")

arab_pre_bt <- get_bt_terms(0, 1, "terror", 200, "Arab Americans", "Indian Americans")
indian_pre_bt <- get_bt_terms(0, 0, "terror", 200, "Arab Americans", "Indian Americans")
```

```{r}
terms2plot_sep(arab_pre_bt, indian_pre_bt, "terror", "Pre-9/11") + terms2plot_sep(arab_post_bt, indian_post_bt, "terror", "Post-9/11") +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 8))

ggsave(here("output", "btterrorsep_ai.png"), width = 12, height = 10)
```

# Arab + Fipilino

## Subsetted data 

```{r}
corpus <- corpus_copy %>%
  filter(group %in% c("Arab", "Filipino")) %>%
  mutate(group = if_else(str_detect(group, "Arab"), 1, 0))
```

## Local embedding and matrix 

```{r}
set.seed(20201008L)
local_glove <- df2vec(corpus)
local_transform <- df2ltm(corpus, local_glove)

save(local_glove, local_transform, 
     file = here("processed_data/context_bg_af.Rdata"))
```

## ALC embedding approach 


```{r}
mod2 <- conText(formula = terror ~ intervention + group, 
          data = corpus, 
          text_var = 'clean_text', 
          pre_trained = local_glove,
          transform = TRUE, 
          transform_matrix = local_transform, 
          bootstrap = TRUE, 
          num_bootstraps = 20, 
          stratify_by = c('intervention', 'group'),
          permute = TRUE, 
          num_permutations = 200, 
          window = 6, 
          valuetype = 'fixed', 
          case_insensitive = TRUE, 
          hard_cut = FALSE, 
          verbose = FALSE)

plot_tibble2 <- mod2$normed_betas %>% 
  mutate(Coefficient = c("9/11 attacks", "Arab American")) %>% 
  mutate(Coefficient = factor(Coefficient, levels = Coefficient))

kableExtra::kable(plot_tibble2)
```

Coefficient	Normed_Estimate	Std.Error	Empirical_Pvalue
9/11 attacks	0.6490103	0.0189908	0
Arab American	1.2189990	0.0076688	0

```{r}
reg_plot2 <- plot_tibble2 %>%
  ggplot(aes(x = Coefficient, y = Normed_Estimate)) + 
  geom_bar(position = position_dodge(), 
    stat = "identity", width = 0.5) + 
  geom_errorbar(aes(ymin = Normed_Estimate - 
    1.96 * Std.Error, ymax = Normed_Estimate + 1.96 * Std.Error), size = 0.75, width = 0.15, 
    position = position_dodge(0.9)) + 
  ylab("Norm of beta hats") + 
  theme(axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 1),
          axis.text.y = element_text(size = 10)) +
  labs(title = "Arab and Filipino American newspaper comparison",
       subtitle = "Keyword: Terror")

reg_plot2

ggsave(here("output", "embedreg_af.png"))
```

## Nearest neighbors 

```{r}
set.seed(20201008L)
arab_post_bt <- get_bt_terms(1, 1, "terror", 200, "Arab Americans", "Filipino Americans")
indian_post_bt <- get_bt_terms(1, 0, "terror", 200, "Arab Americans", "Filipino Americans")

arab_pre_bt <- get_bt_terms(0, 1, "terror", 200, "Arab Americans", "Filipino Americans")
indian_pre_bt <- get_bt_terms(0, 0, "terror", 200, "Arab Americans", "Filipino Americans")
```

```{r}
terms2plot_sep(arab_pre_bt, indian_pre_bt, "terror", "Pre-9/11") + terms2plot_sep(arab_post_bt, indian_post_bt, "terror", "Post-9/11") + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 8))

ggsave(here("output", "btterrorsep_af.png"), width = 12, height = 10)
```

# Arab + AAPI

## Subsetted data 

```{r}
corpus <- corpus_copy %>%
  filter(group %in% c("Arab", "AAPI")) %>%
  mutate(group = if_else(str_detect(group, "Arab"), 1, 0))
```

## Local embedding and matrix 

```{r}
set.seed(20201008L)
local_glove <- df2vec(corpus)
local_transform <- df2ltm(corpus, local_glove)

save(local_glove, local_transform, 
     file = here("processed_data/context_bg_aa.Rdata"))
```

## ALC embedding approach 


```{r}
mod3 <- conText(formula = terror ~ intervention + group, 
          data = corpus, 
          text_var = 'clean_text', 
          pre_trained = local_glove,
          transform = TRUE, 
          transform_matrix = local_transform, 
          bootstrap = TRUE, 
          num_bootstraps = 20, 
          stratify_by = c('intervention', 'group'),
          permute = TRUE, 
          num_permutations = 200, 
          window = 6, 
          valuetype = 'fixed', 
          case_insensitive = TRUE, 
          hard_cut = FALSE, 
          verbose = FALSE)

plot_tibble3 <- mod3$normed_betas %>% 
  mutate(Coefficient = c("9/11 attacks", "Arab American")) %>% 
  mutate(Coefficient = factor(Coefficient, levels = Coefficient))

kable(plot_tibble3)

mean(mod1$normed_betas$Normed_Estimate[1]/mod1$normed_betas$Normed_Estimate[2],
mod2$normed_betas$Normed_Estimate[1]/mod2$normed_betas$Normed_Estimate[2],
mod3$normed_betas$Normed_Estimate[1]/mod3$normed_betas$Normed_Estimate[2])
```
Coefficient	Normed_Estimate	Std.Error	Empirical_Pvalue
9/11 attacks	0.6490103	0.0189908	0
Arab American	1.2189990	0.0076688	0

```{r}
reg_plot3 <- plot_tibble3 %>%
  ggplot(aes(x = Coefficient, y = Normed_Estimate)) + 
  geom_bar(position = position_dodge(), 
    stat = "identity", width = 0.5) + 
  geom_errorbar(aes(ymin = Normed_Estimate - 
    1.96 * Std.Error, ymax = Normed_Estimate + 1.96 * Std.Error), size = 0.75, width = 0.15, 
    position = position_dodge(0.9)) + 
  ylab("Norm of beta hats") + 
  theme(axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 1),
          axis.text.y = element_text(size = 10)) +
  labs(title = "Arab and Asian American newspaper comparison",
       subtitle = "Keyword: Terror")

reg_plot3

ggsave(here("output", "embedreg_aa.png"))

(reg_plot1) /
(reg_plot2) /
(reg_plot3) +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 8))

ggsave(here("output", "embedreg_all.png"),
       height = 15)
```

## Nearest neighbors 

```{r}
set.seed(20201008L)
arab_post_bt <- get_bt_terms(1, 1, "terror", 200, "Arab Americans", "Asian Americans")
indian_post_bt <- get_bt_terms(1, 0, "terror", 200, "Arab Americans", "Asian Americans")

arab_pre_bt <- get_bt_terms(0, 1, "terror", 200, "Arab Americans", "Asian Americans")
indian_pre_bt <- NULL
```

```{r}
terms2plot_sep(arab_pre_bt, indian_pre_bt, "terror", "Pre-9/11") + terms2plot_sep(arab_post_bt, indian_post_bt, "terror", "Post-9/11") +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 8))

ggsave(here("output", "btterrorsep_aa.png"), width = 12, height = 10)
```