---
title: "ITS design analysis"
author: "Jae Yeon Kim"
output:
  html_document: 
    toc: true
    theme: united
---

## 0. Setup

I tweaked the global option of the R Markdown to enlarge figures produced by ggplot2.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, 
                      echo = FALSE, warning = FALSE, message = FALSE) # global setting for enlarging image size
```

```{r}

# Clean up the environment

# rm(list = ls())

# Import libraries (adapted from this link: https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # for the tidyverse framework 
        splitstackshape, # for stacking and reshaping datasets 
        tsModel, # for specifying time series regression models
        lmtest, # for testing linear regression models
        Epi, # for statistical analysis in epidemology 
        splines, # for spline regression
        vcd, # for visualizing categorical variable 
        nlme, # for linear and nonlinear mixed effects models 
        zoo, # S3 infrastructure for regular and irregular time series 
        TTR, # for constructing technical trading rules
        ggpmisc, # for detecting peaks and valleys 
        broom, # for tidying model objects 
        modelr, # for modeling 
        forecast, # for forecasting 
        ggseas, # for seasonal and decomposition on the fly
        itsadug, # for interpreting time series and autocorrelated data 
        mgcv, # for mixed GAM Computation Vehicle with Automatic Smoothness Estimation
        tseries, # for computational financial analysis
        mcp, # for regression with multiple change points 
        ggthemes, # for fancy ggplot themes
        ggpubr) # for arranging plots 
```

## 1. Import files

Unfortunately, I cannot share the original data because they are proprietary. Proquest holds the copyrights. 

```{r include=FALSE}

# Import files 

unlabeled <- read_csv("/home/jae/muslim_newspapers-selected/code/unlabeled_articles.csv")
sample <- read_csv("/home/jae/muslim_newspapers-selected/processed_data/sample_articles.csv")
results <- read_csv("/home/jae/muslim_newspapers-selected/processed_data/final_values_predicted.csv")

```

## 2. Merging dataframes 


```{r}

# Replace NAs with 0s in sample articles 

sample$expanding[is.na(sample$expanding)] <- 0
sample$distancing[is.na(sample$distancing)] <- 0
sample$assimilating[is.na(sample$assimilating)] <- 0

# Collapsing three variables into one 

sample$domestic <- ifelse(sample$expanding == 1 | sample$distancing == 1 | sample$assimilating == 1, 1, 0)

# Create domestic variable for unlabeled and apply predicted values to the variable 

unlabeled$domestic <- results$`0`

# Select key variables 

sample_selected <- dplyr::select(sample, 
              source,
              intervention,
              date,
              domestic)

labeled_selected <- dplyr::select(unlabeled, 
              source, 
              intervention,
              date,
              domestic)

# Row bind the two dataframes  

df <- bind_rows(sample_selected, labeled_selected)

```

## 3. Descriptive analysis

### 3.1. Data wrangling

```{r}

# Create group variable based on newspaper names 

df$group <- ifelse(str_detect(df$source, "India"), "Indian Americans", "Arab Americans")

# Check date variable 

paste("the class of date is", class(df$date))

# Convert date into date object 

df$date <- as.Date(as.character(df$date), "%Y%m%d") 

# Recode values in domestic variable 

df$domestic <- as.character(df$domestic) 

df$domestic[df$domestic == 1] <- "Domestic"
df$domestic[df$domestic == 0] <- "Non-domestic"

```

### 3.2. Data visualization

#### 3.1. Raw data 

```{r}

# Grouping and summarizing data 

df_grouped <- df %>%
  group_by(date, domestic, group) %>% # group by 
  dplyr::summarize(n = n()) # summarize 

# Raw plot 

df_grouped %>%
  ggplot(aes(x = date, y = n)) +
    geom_line(size = 1) + # line plot
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") + # vertical line
    scale_y_continuous(breaks= scales::pretty_breaks()) + # pretty breaks on transformed scale 
    facet_wrap(group~domestic, scale = "free_y") + # facetting, y scale is free 
    labs(x = "Date",
         y = "Publication count",
         col = "Issue focus",
         title = "9/11 and Minority Political Interests",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch") + # labels 
    theme_fivethirtyeight() # theme 

# Save plot 

ggsave("/home/jae/ITS-Text-Classification/output/raw_data_plot.png")

```

#### 3.2. No outliers and missing values 

I adapted the code from this Oracle blog post to remove outliers and impute missing values. As the number of missing values in the data is 0, this process focuses on removing outliers. The plot shows that a couple of outliers disappeared in the updated data. 

```{r}

# checking whether there's NA
paste("The number of missing values in the data is", sum(is.na(df_grouped)))

# Clean the dependent variable

count_ts <- ts(df_grouped[, c('n')])

df_grouped$count_ts <- tsclean(count_ts)

# Cleaned plot 

df_grouped %>%
  ggplot(aes(x = date, y = count_ts)) +
    geom_line(size = 1) + # line plot
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") + # vertical line
    scale_y_continuous(breaks= scales::pretty_breaks()) + # pretty breaks on transformed scale 
    facet_wrap(group~domestic, scale = "free_y") + # facetting, y scale is free 
    labs(x = "Date",
         y = "Publication count",
         col = "Issue focus",
         title = "9/11 and Minority Political Interests",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch") + # labels 
    theme_fivethirtyeight() # theme 

# Save plot 

ggsave("/home/jae/ITS-Text-Classification/output/cleaned_data_plot.png")
```


## 4. Interrupted time series design analysis 

### 4.1. Base model

```{r}

# Create intervention variable 

df_grouped$intervention <- ifelse(df_grouped$date < as.Date("2001-09-11"), 0, 1)

# Divide data 

df_domestic <- df_grouped %>%
  filter(domestic == "Domestic") 

df_nondomestic <- df_grouped %>%
  filter(domestic != "Domestic") 

# Create a function for non-adjusted models 

visualize_its_base <- function(input){
  
  # Apply Poisson regression model 
  
  model <- glm(count_ts ~ intervention + date + group, family = poisson, data = input)
  
  # Check dispersion 
  print(summary(model)$dispersion)
  
  # Check ci
  print(ci.exp(model))
  
  # Make predictions 
  
  input$pred <- predict(model, type = "response", input)
  
  # Create confidence intervals  
  
  ilink <- family(model)$linkinv # Extracting the inverse link from parameter objects 
  
  # Combined prediction outputs 
  
  input <-predict(model, input, se.fit = TRUE)[1:2] %>%
    bind_cols(input) %>%
    mutate(
      upr = ilink(fit + (2 * se.fit)),
      lwr = ilink(fit - (2 * se.fit)))
  
  # Visualize the outcome 
  
  input %>%
    ggplot(aes(x = date, y = count_ts)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~group) +
    geom_line(aes(y = pred), size = 1) +
    ggthemes::theme_fivethirtyeight() +
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") +
    ggthemes::theme_fivethirtyeight() +
    labs(x = "Date",
         y = "Publication count",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch") +
    scale_y_continuous(breaks= scales::pretty_breaks()) +
    geom_ribbon(aes(ymin = lwr, ymax = upr),
                alpha = 0.3, color = "blue")
}

# Visualize ITS analysis result for each subset of the data 

ggarrange(visualize_its_base(df_domestic) + ggtitle("9/11 and Minority Domestic Political Interests"),
          visualize_its_base(df_nondomestic) + ggtitle("9/11 and Minority International Political Interests"),
          nrow = 2, ncol =1)

ggsave("/home/jae/ITS-Text-Classification/output/its_base_plot.png")
```
### 4.2. Check for autocorrelation

The base model is naive. To make it more robust, first, I assess the correlation between the series and its time lags (autocorrelation). In both cases, ACF (correlation a time series and its lags) test shows only a handful of lags have statistically significant estimated correlation coefficients. As expected, PACF (correlation between a time series and its lags unexplained by previous lags) test shows overall even small coefficients. 

```{r}

check_autocorrelation_acf <- function(input){
  
  # Model 
  
  model <- glm(count_ts ~ intervention + date + group + harmonic(date, 2, length(input$date)), family = quasipoisson, data = input) 
  
  # Autocorrelation functions 
  
  pacf <- ggAcf(resid(model)) +
    theme_fivethirtyeight()

}

check_autocorrelation_pacf <- function(input){
  
  # Model 
  
  model <- glm(count_ts ~ intervention + date + group + harmonic(date, 2, length(input$date)), family = quasipoisson, data = input) 
  
  # Autocorrelation functions 
  
  pacf <- ggPacf(resid(model)) +
    theme_fivethirtyeight()

}
```

```{r echo=FALSE}

# Apply to each data

ggarrange(check_autocorrelation_acf(df_domestic) + ggtitle("9/11 and Minority Domestic Political Interests (ACF)"), 
          check_autocorrelation_acf(df_nondomestic) + ggtitle("9/11 and Minority International Political Interests (ACF)"),
           nrow = 2, ncol =1)

ggarrange(check_autocorrelation_pacf(df_domestic) + ggtitle("9/11 and Minority Domestic Political Interests (PACF)"), 
          check_autocorrelation_pacf(df_nondomestic) + ggtitle("9/11 and Minority International Political Interests (PACF)"),
           nrow = 2, ncol =1)

```

### 4.3. Adjusted for over-dispersion and seasonality

As the next step, I adjusted the base model for over-dispersion and seasonality to examine whether these steps make any difference. I adapted some code from [Lopez Bernal IJE 2017](https://github.com/gasparrini/2017_lopezbernal_IJE_codedata) to do so. 

```{r}

# A new function which is adjusted for over-dispersion and seasonality

visualize_its_adjusted_od_st <- function(input){
  
  # Apply quasi-Poisson model to avoid over-dispersion: the conditional variance > the conditional mean -> as a consequence cis are likely to be narrow. See the following link: https://stats.idre.ucla.edu/stata/dae/poisson-regression/ 
  
  model <- glm(count_ts ~ intervention + date + group + harmonic(date, 2, length(input$date)), family = quasipoisson, data = input) # harmonic term is added for accounting for seasonality
  
  # Check dispersion 
  print(summary(model)$dispersion)
  
  # Check ci
  print(ci.exp(model))
  
  # Make predictions 
  
  input$pred <- predict(model, type = "response", input)
  
  # Create confidence intervals  
  
  ilink <- family(model)$linkinv # Extracting the inverse link from parameter objects 
  
  # Combined prediction outputs 
  
  input <-predict(model, input, se.fit = TRUE)[1:2] %>%
    bind_cols(input) %>%
    mutate(
      upr = ilink(fit + (2 * se.fit)),
      lwr = ilink(fit - (2 * se.fit)))
  
  # Visualize the outcome 
  
  input %>%
    ggplot(aes(x = date, y = count_ts)) +
    geom_point(alpha = 0.2) +
    facet_wrap(~group) +
    geom_line(aes(y = pred), size = 1) +
    ggthemes::theme_fivethirtyeight() +
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") +
    ggthemes::theme_fivethirtyeight() +
    labs(x = "Date",
         y = "Publication count",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch") +
    scale_y_continuous(breaks= scales::pretty_breaks()) +
    geom_ribbon(aes(ymin = lwr, ymax = upr),
                alpha = 0.3, color = "blue")
}

# Visualize each result 

ggarrange(visualize_its_adjusted_od_st(df_domestic) + ggtitle("9/11 and Minority Domestic Political Interests"), 
          visualize_its_adjusted_od_st(df_nondomestic) + ggtitle("9/11 and Minority International Political Interests"),
           nrow = 2, ncol =1)

ggsave("/home/jae/ITS-Text-Classification/output/its_adjusted_plot.png")

```