---
title: "ITS design analysis"
author: "Jae Yeon Kim"
output:
html_document:
  toc: True
  theme: united
  number_sections: True
---

# Setup

```{r}

# Import libraries 

pacman::p_load(
        tidyverse, # the tidyverse framework 
        splitstackshape, # stacking and reshaping datasets 
        tsModel, # specifying time series regression models
        lmtest, # testing linear regression models
        Epi, # statistical analysis in epidemology 
        splines, # spline regression
        vcd, # visualizing categorical variable 
        nlme, # linear and nonlinear mixed effects models 
        zoo, # S3 infrastructure regular and irregular time series 
        simpleboot, # bootstrapping 
        TTR, # constructing technical trading rules
        ggpmisc, # detecting peaks and valleys 
        broom, # tidying model objects 
        modelr, # modeling 
        forecast, # forecasting 
        ggseas, # seasonal and decomposition on the fly
        itsadug, # interpreting time series and autocorrelated data 
        mgcv, # mixed GAM Computation Vehicle with Automatic Smoothness Estimation
        tseries, # computational financial analysis
        mcp, # regression with multiple change points
        lawstat, # testing stats in biostat, public policy, and law
        sarima, # simulation and prediction with seasonal ARIMA models  
        car, # Durbin Watson test 
        tidyr, # tidying messy daa 
        AICcmodavg, # computing predicted values and standard errors 
        MuMIn, # selecting models
        ggthemes, # fancy ggplot themes
        ggpubr, # arranging plots 
        stargazer, # regression table 
        here, # reproducibility 
        patchwork) # rearranging ggplot 

# devtools::install_github("jaeyk/makereproducible")
library(makereproducible)

# Import R scripts

script_list <- list.files(paste0(here::here(), "/functions"),
  pattern = "*.r|*.R",
  full.names = TRUE
)

for (i in 1:length(script_list))
{
  source(script_list[[i]])
}

# for publication-friendly theme
theme_set(theme_pubr())

```

# Importing files

Unfortunately, I cannot share the original data because they are proprietary. Proquest holds the copyrights. 

```{r include=FALSE}

# Import files 

unlabeled <- read_csv(make_here("/home/jae/muslim_newspapers-selected/raw_data/unlabeled_articles.csv"))

sample <- read_csv(make_here("/home/jae/muslim_newspapers-selected/raw_data/sample_articles.csv"))

results <- read_csv(make_here("/home/jae/muslim_newspapers-selected/processed_data/predicted.csv"))

```

# Merging dataframes 


```{r}

# Replace NAs with 0s in sample articles 

sample$expanding[is.na(sample$expanding)] <- 0
sample$distancing[is.na(sample$distancing)] <- 0
sample$assimilating[is.na(sample$assimilating)] <- 0

# Collapsing three variables into one 

sample$domestic <- ifelse(sample$expanding == 1 | sample$distancing == 1 | sample$assimilating == 1, 1, 0)

# Create domestic variable for unlabeled and apply predicted values to the variable 

unlabeled$domestic <- results$`0`

# Select key variables 

sample_selected <- dplyr::select(sample, 
              source,
              intervention,
              date,
              domestic,
              text)

labeled_selected <- dplyr::select(unlabeled, 
              source, 
              intervention,
              date,
              domestic,
              text)

# Row bind the two dataframes  

df <- bind_rows(sample_selected, labeled_selected)

```

# Descriptive analysis

## Data wrangling

If you want to replicate the analysis, you can start from here using `df.csv` saved in `processed_data` directory..

```{r}

# df <- read_csv("/home/jae/ITS-Text-Classification/processed_data.df.csv")

# Check date variable 

paste("the class of date is", class(df$date))

# Convert date into date object 

df$date <- as.Date(as.character(df$date), "%Y%m%d") 

# Recode values in domestic variable 

df$domestic <- as.character(df$domestic) 

df$domestic[df$domestic == 1] <- "Domestic"
df$domestic[df$domestic == 0] <- "International"

# Create group variable based on newspaper names 

df$group <- ifelse(str_detect(df$source, "India"), "Indian Americans", "Arab Americans")

# Save the processed data 

write.csv(df, make_here("/home/jae/ITS-Text-Classification/processed_data/df.csv"))

```

## Data visualization

### Raw data 

```{r}

# Grouping and summarizing data 

df_grouped <- df %>%
  group_by(date, domestic, group) %>% # group by 
  dplyr::summarize(n = n()) %>% # summarize 
  as.data.frame()

# Raw plot 

df_grouped %>%
  ggplot(aes(x = date, y = n)) +
    geom_line() + # line plot
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") + # vertical line
    scale_y_continuous(breaks= scales::pretty_breaks()) + # pretty breaks on transformed scale 
    facet_grid(group~domestic) + # facetting, y scale is free 
    labs(x = "Date",
         y = "Publication count",
         col = "Issue focus",
         title = "9/11 and Minority Political Interests",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch") 

# Save plot 

ggsave(make_here("/home/jae/ITS-Text-Classification/output/raw_data_plot.png"), width = 13)

```

### No outliers and missing values 

I adapted the code from this Oracle blog post to remove outliers and impute missing values. As the number of missing values in the data is 0, this process focuses on removing outliers. The plot shows that a couple of outliers disappeared in the updated data. 

```{r}

# checking whether there's NA
paste("The number of missing values in the data is", sum(is.na(df_grouped)))

# Clean the dependent variable

count_ts <- ts(df_grouped[, c('n')])

df_grouped$count_ts <- as.integer(tsclean(count_ts))

# Get rid of n
df_grouped <- df_grouped %>%
  dplyr::select(-n)

# Cleaned plot 

cleaned_domestic_plot <- df_grouped %>%
  filter(domestic == "Domestic") %>%
  ggplot(aes(x = date, y = count_ts)) +
    geom_line() + # line plot
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") + # vertical line
    scale_y_continuous(breaks= scales::pretty_breaks()) + # pretty breaks on transformed scale 
    facet_wrap(~group, scale = "free_y") + # facetting, y scale is free 
    labs(x = "Date",
         y = "Publication count",
         col = "Issue focus",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch")
  
cleaned_nondomestic_plot <- df_grouped %>%
  filter(domestic != "Domestic") %>%
  ggplot(aes(x = date, y = count_ts)) +
    geom_line() + # line plot
    geom_vline(xintercept = as.Date("2001-09-11"), linetype = "dashed", size = 1, color = "red") + # vertical line
    scale_y_continuous(breaks= scales::pretty_breaks()) + # pretty breaks on transformed scale 
    facet_wrap(~group, scale = "free_y") + # facetting, y scale is free 
    labs(x = "Date",
         y = "Publication count",
         col = "Issue focus",
         subtitle = "All articles mentioned Muslims",
         caption = "Source: Ethnic Newswatch")

# Save plot 
  
cleaned_domestic_plot <- cleaned_domestic_plot + ggtitle("9/11 and Minority Domestic Political Interests") + labs(tag = "A", caption = "")

cleaned_nondomestic_plot <- cleaned_nondomestic_plot + ggtitle("9/11 and Minority International Political Interests") + labs(tag = "B")

cleaned_domestic_plot / cleaned_nondomestic_plot

ggsave(make_here("/home/jae/ITS-Text-Classification/output/cleaned_data_plot.png"), height = 8)

```


# Interrupted time series design analysis 

## Base model

```{r}

# Create assignment variable 

df_grouped$intervention <- ifelse(df_grouped$date < as.Date("2001-09-11"), 0, 1)

# Divide data 

df_domestic <- df_grouped %>%
  filter(domestic == "Domestic") 

df_nondomestic <- df_grouped %>%
  filter(domestic != "Domestic") 

# Visualize ITS analysis result for each subset of the data 

its_base_dom_plot <- visualize_base(df_domestic) + ggtitle("9/11 and Minority Domestic Political Interests") + labs(tag = "A", caption = "")

its_base_nondom_plot <- visualize_base(df_nondomestic) + ggtitle("9/11 and Minority International Political Interests") + labs(tag = "B")

its_base_dom_plot / its_base_nondom_plot

ggsave(make_here("/home/jae/ITS-Text-Classification/output/its_base_plot.png"), height = 8)

```
## Check for autocorrelation

The base model is naive. To make it more robust, first, I assess the correlation between the series and its time lags (autocorrelation). In both cases, ACF (correlation a time series and its lags) test shows there exits a weak seasonal trend. 

```{r}

# Create the full date 

all_days <- seq(min(df_grouped$date), max(df_grouped$date), by ="+1 day")

# Turn it into a dataframe 

all_days <- data.frame(date = all_days)

# Filling the missing days 

df_grouped <- all_days %>%
  merge(df_grouped, by = "date", all.x = TRUE)

# Divide data 

df_domestic <- df_grouped %>%
  filter(domestic == "Domestic") 

df_nondomestic <- df_grouped %>%
  filter(domestic != "Domestic") 

```

```{r echo=FALSE}
# Apply to each data
acf_dom <- acf_plot(df_domestic) + ggtitle("Domestic Political Interests") + labs(tag = "A")

acf_nondom <- acf_plot(df_nondomestic) + ggtitle("International Political Interests") + labs(tag = "B")

acf_dom / acf_nondom

ggsave(make_here("/home/jae/ITS-Text-Classification/output/acf_plot.png"))

```


## Parameterizing correlation

The new model parameterizes autocorrelation by accounting for the correlation between the time series data and its time lags. `corARMA() function` defines correlation structure. `p` argument specifies the autoregressive order, and `q` argument specifies the moving average order of the ARMA structure. I then find the combination of `p` and `q` that yields the minimum Akaike Information Criterion (AIC).

```{r eval=FALSE, include=FALSE}

pq_domestic <- mapply(correct_ac_domestic, c(1,2,3), c(1))

pq_nondomestic <- mapply(correct_ac_nondomestic, c(1,2,3), c(1))

pq_domestic

pq_nondomestic
```

## Visualization 

```{r}
# Visualize each result in the scatted plot 

its_adj_dom_plot <- visualize_adj(df_domestic, 3, 1) + ggtitle("9/11 and Minority Domestic Political Interests") + labs(caption = "", tag = "A")

its_adj_nondom_plot <- visualize_adj(df_nondomestic, 3, 1) + ggtitle("9/11 and Minority International Political Interests") + labs(tag = "B")

its_adj_dom_plot / its_adj_nondom_plot

ggsave(here("output", "its_adjusted_plot.png"), height = 8)

```

## Bootstrapping analysis 

```{r}

df_domestic <- df_domestic %>%
    mutate(year = extract_year(df1))

df_nondomestic <- df_nondomestic %>%
    mutate(year = extract_year(df2))

plot_boot <- plot_boot_analysis(df_domestic,
                   df_nondomestic)

plot_boot

ggsave(here("output", "boot_analysis.png"))

```

## Regression table

### OLS

```{r}

dom_output_ols <- lm(count_ts ~ intervention +  date + group, 
               data = df_domestic) 

nondom_output_ols <- lm(count_ts ~ intervention +  date + group, 
               data = df_nondomestic)

stargazer(dom_output_ols, nondom_output_ols,
          title = "ITS design analysis results",
          dep.var.labels = c("The publication count for Muslim-related articles on"),
          header = FALSE,
          single.row = TRUE,
          column.labels = c("Domestic politics",
                            "International politics"),
          covariate.labels = c("Intervention",
                               "Date",
                               "Indian Americans"),
          model.numbers = FALSE)

```

### GLS 

```{r}

dom_output_gls <- gls(count_ts ~ intervention +  date + group, 
               data = df_domestic,
               correlation = corARMA(p= 3, q = 1, form = ~ date | group)) 

nondom_output_gls <- gls(count_ts ~ intervention +  date + group, 
               data = df_nondomestic,
               correlation = corARMA(p= 3, q = 1, form = ~ date | group)) 

stargazer(dom_output_gls, nondom_output_gls,
          title = "ITS design analysis results",
          dep.var.labels = c("The publication count for Muslim-related articles on"),
          header = FALSE,
          single.row = TRUE,
          column.labels = c("Domestic politics",
                            "International politics"),
          covariate.labels = c("Intervention",
                               "Date",
                               "Indian Americans"),
          model.numbers = FALSE)
```