---
title: "Additional text analysis"
author: "Jae Yeon Kim"
output:
html_document:
  toc: True
  theme: united
  number_sections: True
---

# Setup

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # the tidyverse framework
        lubridate, # wrangling date and time
        ggpubr, # arranging ggplots
        ggthemes, # fancy ggplot themes
        tidytext, # tidytext
        patchwork, # arranging images,
        purrr, # functional programming
        here, # reproducibility
        httr, # httr connection 
        jsonlite, # parsing JSON
        glue, # gluing objects and strings         
        rio, # import and export files  
        forecast # forecasting 
)

devtools::install_github("jaeyk/rnytapi", dependencies = TRUE)

library(rnytapi)
```

```{r}
# Import R scripts

script_list <- list.files(here("functions"),
  pattern = "*.r|*.R",
  full.names = TRUE
)

walk(script_list, source)
```

# Collecting data using the NYT API

```{r}
#Sys.setenv(nyt_key = "<insert key>")
key <- Sys.getenv("nyt_key")

# Parameters 

begin_year <- 1996:2005
end_year <- 1997:2006
term <- "muslim+muslims"
```

I need to split the date ranges to get around the NYT API policy on pagination (max 200 pages for a search result).

```{r}
df1996 <- extract_all(term = 'muslim+muslims', begin_date = '19960911', end_date = '19970911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df1997 <- extract_all(term = 'muslim+muslims', begin_date = '19970911', end_date = '19980911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df1998 <- extract_all(term = 'muslim+muslims', begin_date = '19980911', end_date = '19990911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df1999 <- extract_all(term = 'muslim+muslims', begin_date = '19990911', end_date = '20000911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2000 <- extract_all(term = 'muslim+muslims', begin_date = '20000911', end_date = '20010911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

df2001a <- extract_all(term = 'muslim+muslims', begin_date = '20010911', end_date = '20011231', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2001b <- extract_all(term = 'muslim+muslims', begin_date = '20021231', end_date = '20030311', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2001c <- extract_all(term = 'muslim+muslims', begin_date = '20020311', end_date = '20020911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

df2002a <- extract_all(term = 'muslim+muslims', begin_date = '20020911', end_date = '20021231', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2002b <- extract_all(term = 'muslim+muslims', begin_date = '20021231', end_date = '20030311', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2002c <- extract_all(term = 'muslim+muslims', begin_date = '20030311', end_date = '20030911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

df2003a <- extract_all(term = 'muslim+muslims', begin_date = '20030911', end_date = '20031231', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2003b <- extract_all(term = 'muslim+muslims', begin_date = '20031231', end_date = '20040311', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2003c <- extract_all(term = 'muslim+muslims', begin_date = '20040311', end_date = '20040911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

df2004a <- extract_all(term = 'muslim+muslims', begin_date = '20040911', end_date = '20041231', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2004b <- extract_all(term = 'muslim+muslims', begin_date = '20051231', end_date = '20050311', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2004c <- extract_all(term = 'muslim+muslims', begin_date = '20050311', end_date = '20050911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

df2005a <- extract_all(term = 'muslim+muslims', begin_date = '20050911', end_date = '20051231', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2005b <- extract_all(term = 'muslim+muslims', begin_date = '20051231', end_date = '20060311', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2005c <- extract_all(term = 'muslim+muslims', begin_date = '20060311', end_date = '20060711', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')
df2005d <- extract_all(term = 'muslim+muslims', begin_date = '20060711', end_date = '20060911', key = 'lJWFqmFXKLE8yoxN95xLjnyqMFk67a5I')

save(list = ls(pattern = "^df"), file = here("processed_data/nyt_parts.Rdata"))

df <- bind_rows(mget(ls(pattern = "^df")))

df <- df %>%
  # Filter non-successful search results
  filter(status == "OK") %>%
  # Remove duplicates 
  distinct()

write_rds(df, here("processed_data/nyt_articles.Rdata"))
```

# Munging data 

```{r}
df <- read_rds(here("processed_data/nyt_articles.Rdata"))

# Rename columns 
colnames(df) <- str_remove(colnames(df), "response.docs.")
```


```{r}
# Select columns and filter rows 
df <- df %>%
  select(pub_date, section_name, subsection_name) %>%
  filter(!(section_name %in% c("Style", "Business Day", "Books", "Arts", "Magazine", "Movies", "Theater", "Sports", "Your Money", "Science", "Technology", "Food", "Health", "Real Estate", "Job Market", "Great Homes & Destinations", "Automobiles", "Fashion & Style", "Home & Garden", "Travel")))

nrow(df)
```


```{r}
# Format date column and rename it
df$pub_date <- lubridate::ymd(str_replace(df$pub_date, "T.*", ""))

df <- df %>% rename(date = pub_date)
```


```{r}
# Filter rows and mutate domestic column 
df <- df %>%
  mutate(domestic = ifelse(section_name == "World", "International", "Domestic"))

df$intervention <- ifelse(df$date > as.Date("2001-09-11"), 1, 0)

table(df$section_name)
```

# Data visualization

```{r}
comp_df <- read.csv(here("processed_data/df.csv"))
comp_df$date <- as.Date(comp_df$date)
```

## Raw data 

```{r}
domestic_plot <- ts_df(df) %>%
  filter(domestic == "Domestic") %>%
  visualize_raw() +
  ggtitle("Majority Interests in Domestic News on Muslims") + 
  labs(tag = "A", caption = "") +
  ylim(c(0,17))

nondomestic_plot <- ts_df(df) %>%
  filter(domestic != "Domestic") %>% 
  visualize_raw() +
  ggtitle("Majority Interests in International News on Muslims") + 
  labs(tag = "C", 
       caption = "Source: New York Times") +
  ylim(c(0,17))

comp_domestic_plot <- ts_df(comp_df) %>%
  filter(domestic == "Domestic") %>% 
  visualize_raw() +
  ggtitle("Minority Interests in Doemstic News on Muslims") + 
  labs(tag = "B", caption = "") +
  ylim(c(0,17))

comp_nondomestic_plot <- ts_df(comp_df) %>%
  filter(domestic != "Domestic") %>%
  visualize_raw() +  
  ggtitle("Minority Interests in International News on Muslims") + 
  labs(tag = "D", caption = "Source: Ethnic NewsWatch") +
  ylim(c(0,17))

(domestic_plot + comp_domestic_plot) /
(nondomestic_plot + comp_nondomestic_plot) 

ggsave(here("output/nyt_ethnic_raw_comp.png"), height = 8)
```

## ITS analysis

### Base model

```{r}
# Create assignment variable 
df_grouped <- ts_df(df)
comp_df_grouped <- group_df(comp_df)

# Divide data 

df_domestic <- df_grouped %>%
  filter(domestic == "Domestic") 
comp_df_domestic <- comp_df_grouped %>%
  filter(domestic == "Domestic") 

df_nondomestic <- df_grouped %>%
  filter(domestic != "Domestic") 
comp_df_nondomestic <- comp_df_grouped %>%
  filter(domestic != "Domestic")
```


```{r}
# Visualize ITS analysis result for each subset of the data 

its_dom_plot <- visualize_placebo(df_domestic) + 
  ggtitle("Majority Interests in Domestic News on Muslims") + 
  labs(tag = "A", caption = "") +
  ylim(c(0,20))
its_nondom_plot <- visualize_placebo(df_nondomestic) + 
  ggtitle("Majority Interests in International News on Muslims") + 
  labs(tag = "C", 
       caption = "Source: New York Times") +
  ylim(c(0,20))

comp_its_dom_plot <- visualize_placebo(comp_df_domestic) + 
  ggtitle("Minority Interests in Doemstic News on Muslims") + 
  labs(tag = "B", caption = "") +
  ylim(c(0,20))

comp_its_nondom_plot <- visualize_placebo(comp_df_nondomestic) + 
  ggtitle("Minority Interests in International News on Muslims") + 
  labs(tag = "D", caption = "Source: Ethnic NewsWatch") +
  ylim(c(0,20))

(its_dom_plot + comp_its_dom_plot) /
(its_nondom_plot + comp_its_nondom_plot)

ggsave(here("output/nyt_ethnic_its_comp.png"), height = 8)
```

# Regression table

```{r}
dom_output_ols <- lm(count_ts ~ intervention + date, 
               data = df_domestic) 

stargazer(dom_output_ols, 
          title = "ITS design analysis results",
          dep.var.labels = c("The publication count for Muslim-related articles on"),
          header = FALSE,
          single.row = TRUE,
          column.labels = c("Domestic politics",
                            "International politics"),
          covariate.labels = c("Intervention",
                               "Date"),
          model.numbers = FALSE)
```

\begin{table}[!htbp] \centering 
  \caption{ITS design analysis results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & The publication count for Muslim-related articles on \\ 
 & Domestic politics \\ 
\hline \\[-1.8ex] 
 Intervention & 1.977$^{***}$ (0.164) \\ 
  Date & 0.0001$^{*}$ (0.0001) \\ 
  Constant & 0.337 (0.831) \\ 
 \hline \\[-1.8ex] 
Observations & 2,684 \\ 
R$^{2}$ & 0.211 \\ 
Adjusted R$^{2}$ & 0.210 \\ 
Residual Std. Error & 2.142 (df = 2681) \\ 
F Statistic & 358.635$^{***}$ (df = 2; 2681) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

# Extract and export R code 

```{r eval=FALSE}
knitr::purl(input = here("code", "07_additional_text_analysis.Rmd"), 
            output = here("code", "07_additional_text_analysis.r"))
```

